---
title: "BT2201 Finance Project Notebook"
output:
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

This notebook quantifies the analysis we conducted to arrive at our optimal asset allocations.


## 1. Determine Investment Policy

Which products should be offered to a typical Japanese retail investor


### Risk Appetite

The typical Japanese retail investor is risk averse. Many older Japanese investors lived through the Asian Financial Crisis which saw a huge asset bubble and subsequent crash in Japanese financial markets. Those who invested money right at the peak of the asset bubble would have lost a considerable amount of money. Japan also entered many years of deflation afterwards.

Therefore, a typical Japanese retail investor is distinct from an American or European retail investor in that they have experienced more market downside and less economic euphoria. We expect that they will have a more conservative risk appetite and less tolerance for portfolio drawdown.


### Objective Function (CHANGE TO EFFICIENT RETURN)

Given the conditions described above, we choose to adopt the *Efficient Risk* or *Markowitz Portfolio*

This means we minimise risk for a target level of return.

<<<<<<< Updated upstream
(OR find an objective function from here)
https://pyportfolioopt.readthedocs.io/en/latest/MeanVariance.html 

Target Return: Global Average Inflation + 1% = 4.5%
https://www.statista.com/statistics/256598/global-inflation-rate-compared-to-previous-year/

Constraints:

1. Long only
2. Maximum weight of 20% per ETF
=======
For a start, maximise Sharpe:

$min \ \sigma(R) \\ s.t. E(R) = R_{target}$
>>>>>>> Stashed changes


### Amount
As stated in the preamble, investable amount is **JPY 100,000**.

<<<<<<< Updated upstream
### Choice of Assets

We start with the basket of ETFs provided

- BIV: US INTERMEDIATE BOND
- VCSH: US INVESTMENT GRADE BOND
- BNDX: GLOBAL BOND ETF
- VNQ: US REIT
- JP 1343: JREIT
- JP 1555: AU REIT
- SPDR: US STOCK
- VT: GLOBAL STOCK
- HVST AU: EQUITY DIVIDEND ETF AU

??? Analyse core characteristics 
- Fees --> Constraints???
- Currency --> Multiply forex time series
- Liquidity --> EDA?
- BM and TE --> ??


??? What others (is this qualitative)
- Vanguard Tech ETF
=======
>>>>>>> Stashed changes


## 2. Security Analysis

Pull data for tickers described above.
```{r}
#install quantmod, xml2
require(quantmod)

```

```{r}
<<<<<<< Updated upstream


=======
#new universe 
# ETF Data
>>>>>>> Stashed changes
global_etf = c('BIV', # US INTERMEDIATE BOND
            'VCSH',# US INVESTMENT GRADE BOND
            'BNDX',# GLOBAL BOND ETF
            'VNQ', #US REIT
            'VT', #GLOBAL STOCK'
            'SPY' #US STOCK (SPDR)
)

j_etf = c('1328.T','1343.T')

new_etf_universe= c(
  'VTI',
  'VEA',
  'VGT',
  'XLF',
  'XLE',
  'XLY',
  'VAW',
  'GLD',
  'REM',
  'IVLU',
  'VWOB',
  'PDBC',
  'GSG',
  'BIV', # US INTERMEDIATE BOND
  'VCSH',# US INVESTMENT GRADE BON
  'BNDX',# GLOBAL BOND ETF
  'VNQ', #US REIT
  'SPY', #US STOCK (SPDR)
  '1615.T',
  'DXJ'
)

            
getSymbols(new_etf_universe, auto.assign = T)
getSymbols(j_etf, auto.assign = T, src='yahooj')
<<<<<<< Updated upstream
getSymbols(au_etf, auto.assign = T)
=======

```


```{r}
# Exchange Rate Data
library(priceR)
usd_jpy = historical_exchange_rates('USD', to='JPY', start_date='2007-01-01', end_date='2021-11-03')
usd_jpy = as.xts(usd_jpy$one_USD_equivalent_to_x_JPY, order.by=as.Date(usd_jpy$date))

# Convert USA currency adjusted prices to JPY

BIV$BIV.Adjusted = BIV$BIV.Adjusted * usd_jpy
VCSH$VCSH.Adjusted = VCSH$VCSH.Adjusted * usd_jpy
BNDX$BNDX.Adjusted = BNDX$BNDX.Adjusted * usd_jpy
VNQ$BNQ.Adjusted = VNQ$VNQ.Adjusted * usd_jpy 
VT$VT.Adjusted = VT$VT.Adjusted * usd_jpy
SPY$SPY.Adjusted = SPY$SPY.Adjusted * usd_jpy

aud_jpy = historical_exchange_rates('AUD', to='JPY', start_date='2007-01-01', end_date='2021-11-03')
aud_jpy = as.xts(aud_jpy$one_AUD_equivalent_to_x_JPY, order.by=as.Date(aud_jpy$date))

HVST.AX$HVST.AX.Adjusted = HVST.AX$HVST.AX.Adjusted * aud_jpy
>>>>>>> Stashed changes

```
Find out characteristics of each of all the tickers.

### Plots

```{r}
tickers = list(BIV,VCSH,BNDX,VNQ,VT,SPY,`YJ1343.T`,`YJ1555.T`,HVST.AX)
name = list('BIV','VCSH','BNDX','VNQ','VT','SPY','YJ1343.T','YJ1555.T','HVST.AX')

t = BIV
init.d <- index(t)[1]
e <- t[, 6]/as.numeric(t[init.d, 6])
plot(e, main=names(e))
t = VCSH
init.d <- index(t)[1]
e <- t[, 6]/as.numeric(t[init.d, 6])
plot(e, main=names(e))
t = BNDX
init.d <- index(t)[1]
e <- t[, 6]/as.numeric(t[init.d, 6])
plot(e, main=names(e))
t = VNQ
init.d <- index(t)[1]
e <- t[, 6]/as.numeric(t[init.d, 6])
plot(e, main=names(e))
t = VT
init.d <- index(t)[1]
e <- t[, 6]/as.numeric(t[init.d, 6])
plot(e, main=names(e))
t = SPY
init.d <- index(t)[1]
e <- t[, 6]/as.numeric(t[init.d, 6])
plot(e, main=names(e))
t = `YJ1343.T`
init.d <- index(t)[1]
e <- t[, 6]/as.numeric(t[init.d, 6])
plot(e, main=names(e))
t = `YJ1555.T`
init.d <- index(t)[1]
e <- t[, 6]/as.numeric(t[init.d, 6])
plot(e, main=names(e))
t = `HVST.AX`
init.d <- index(t)[1]
e <- t[, 6]/as.numeric(t[init.d, 6])
plot(e, main=names(e))
```


### Returns
Next, calculate Returns and Volatiliy ($\mu \ and \ \sigma$) for each of the ETFs

```{r}
means = c()
sds = c()
returns = c()
for(i in seq(9)){
  ticker = tickers[i][[1]]
  prices_monthly <- to.monthly(ticker, name=name[i], indexAt = "lastof", OHLC = T)
  return <- ROC(Ad(prices_monthly))
  returns = cbind(returns,return)
  means = c(means, mean(return, na.rm=T))
  sds = c(sds, sd(return, na.rm=T))
}
df = data.frame(unlist(name), means, sds)
colnames(df) = c('ETF','Mu_Monthly', 'Sigma_Monthly')
df
```
```{r}
library(fPortfolio)
library(purrr)
returns = data.frame(returns)

colnames(returns) <- unlist(map(colnames(returns), function(x){unlist(strsplit(x,'[.]'))[1]}))
covdata = cov(returns, use = "complete.obs")

corrdata = cor(returns, use='complete.obs')
heatmap(corrdata)
```
## 3. Portfolio Construction
```{r}

pSpec = portfolioSpec()
setTargetReturn(pSpec) <- (1.045)**(1/12)-1
print(pSpec)

```
```{r}
Constraints = c("minW=c(0,0,0,0,0,0,0,0,0)", "maxW=c(0.2,0.2,0.2,0.2,0.2,0.2,0.2,0.2,0.2)" )
lppData = as.timeSeries(returns[complete.cases(returns),])
ep = efficientPortfolio(data = lppData, spec =  pSpec, constraints=Constraints)
ep
```

```{r}
col <- seqPalette(ncol(lppData), "BuPu")
weightsPie(ep, box = FALSE, col = col)
mtext(text = "Tangency MV Portfolio", side = 3, line = 1.5,
font = 2, cex = 0.7, adj = 0)
weightedReturnsPie(ep, box = FALSE, col = col)
mtext(text = "Tangency MV Portfolio", side = 3, line = 1.5,
font = 2, cex = 0.7, adj = 0)
covRiskBudgetsPie(ep, box = FALSE, col = col)
mtext(text = "Tangency MV Portfolio", side = 3, line = 1.5,
font = 2, cex = 0.7, adj = 0)



```
```{r}
tgPortfolio = ep
par(mfrow = c(2, 2))
col <- rampPalette(ncol(lppData), "purple2green")
weights <- 100 * as.vector(getWeights(tgPortfolio))
weightedReturns <- weights * getMean(tgPortfolio)
covRiskBudgets <- getCovRiskBudgets(tgPortfolio)
names <- colnames(lppData)
barplot(height = weights, names.arg = names, horiz = TRUE, las = 1, col = col)
title(main = "Portfolio Weights", xlab = "Weights %")
barplot(height = weightedReturns, names.arg = names, horiz = TRUE, las = 1, col = col)
title(main = "Weighted Portfolio Returns", xlab = "Weighted Returns %")
barplot(height = weights, names.arg = names, las = 1, col = col)



```
## 4. Portfolio Implementation

```{r}
BIV


```

## 5. Portfolio Evaluation


## 6. Portfolio Revisions


