---
title: "BT2201 Finance Project Notebook"
output:
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

This notebook quantifies the analysis we conducted to arrive at our optimal asset allocations.


## 1. Determine Investment Policy

Which products should be offered to a typical Japanese retail investor


### Risk Appetite

The typical Japanese retail investor is risk averse. Many older Japanese investors lived through the Asian Financial Crisis which saw a huge asset bubble and subsequent crash in Japanese financial markets. Those who invested money right at the peak of the asset bubble would have lost a considerable amount of money. Japan also entered many years of deflation afterwards.

Therefore, a typical Japanese retail investor is distinct from an American or European retail investor in that they have experienced more market downside and less economic euphoria. We expect that they will have a more conservative risk appetite and less tolerance for portfolio drawdown.


### Objective Function

Given the conditions described above, we choose to adopt the *Efficient Risk* or *Markowitz Portfolio*

This means we minimise risk for a target level of return.

(OR find an objective function from here)
https://pyportfolioopt.readthedocs.io/en/latest/MeanVariance.html 

Target Return: Global Average Inflation + 1% = 4.5%
https://www.statista.com/statistics/256598/global-inflation-rate-compared-to-previous-year/

Constraints:

1. Long only
2. Maximum weight of 20% per ETF


### Amount
As stated in the preamble, investable amount is **JPY 100,000**.

### Choice of Assets

We start with the basket of ETFs provided

- BIV: US INTERMEDIATE BOND
- VCSH: US INVESTMENT GRADE BOND
- BNDX: GLOBAL BOND ETF
- VNQ: US REIT
- JP 1343: JREIT
- JP 1555: AU REIT
- SPDR: US STOCK
- VT: GLOBAL STOCK
- HVST AU: EQUITY DIVIDEND ETF AU




## 2. Security Analysis

Pull data for tickers described above.
```{r}
#install quantmod, xml2
require(quantmod)

```

```{r}


global_etf = c('BIV', # US INTERMEDIATE BOND
            'VCSH',# US INVESTMENT GRADE BOND
            'BNDX',# GLOBAL BOND ETF
            'VNQ', #US REIT
            'VT', #GLOBAL STOCK'
            'SPY' #US STOCK (SPDR)
)

j_etf = c('1343.T',  # JREIT (JP 1343)
          '1555.T' # AU REIT (JP 1555)
)
           
au_etf = c('HVST.AX' #EQUITY DIVIDEND ETF AU (HVST AU)
)
            
getSymbols(global_etf, auto.assign = T)
getSymbols(j_etf, auto.assign = T, src='yahooj')
getSymbols(au_etf, auto.assign = T)

```
Find out characteristics of each of all the tickers.

### Plots

```{r}
tickers = list(BIV,VCSH,BNDX,VNQ,VT,SPY,`YJ1343.T`,`YJ1555.T`,HVST.AX)
name = list('BIV','VCSH','BNDX','VNQ','VT','SPY','YJ1343.T','YJ1555.T','HVST.AX')

t = BIV
init.d <- index(t)[1]
e <- t[, 6]/as.numeric(t[init.d, 6])
plot(e, main=names(e))
t = VCSH
init.d <- index(t)[1]
e <- t[, 6]/as.numeric(t[init.d, 6])
plot(e, main=names(e))
t = BNDX
init.d <- index(t)[1]
e <- t[, 6]/as.numeric(t[init.d, 6])
plot(e, main=names(e))
t = VNQ
init.d <- index(t)[1]
e <- t[, 6]/as.numeric(t[init.d, 6])
plot(e, main=names(e))
t = VT
init.d <- index(t)[1]
e <- t[, 6]/as.numeric(t[init.d, 6])
plot(e, main=names(e))
t = SPY
init.d <- index(t)[1]
e <- t[, 6]/as.numeric(t[init.d, 6])
plot(e, main=names(e))
t = `YJ1343.T`
init.d <- index(t)[1]
e <- t[, 6]/as.numeric(t[init.d, 6])
plot(e, main=names(e))
t = `YJ1555.T`
init.d <- index(t)[1]
e <- t[, 6]/as.numeric(t[init.d, 6])
plot(e, main=names(e))
t = `HVST.AX`
init.d <- index(t)[1]
e <- t[, 6]/as.numeric(t[init.d, 6])
plot(e, main=names(e))
```


### Returns
Next, calculate Returns and Volatiliy ($\mu \ and \ \sigma$) for each of the ETFs

```{r}
means = c()
sds = c()
returns = c()
for(i in seq(9)){
  ticker = tickers[i][[1]]
  prices_monthly <- to.monthly(ticker, name=name[i], indexAt = "lastof", OHLC = T)
  return <- ROC(Ad(prices_monthly))
  returns = cbind(returns,return)
  means = c(means, mean(return, na.rm=T))
  sds = c(sds, sd(return, na.rm=T))
}
df = data.frame(unlist(name), means, sds)
colnames(df) = c('ETF','Mu_Monthly', 'Sigma_Monthly')
df
```
```{r}
library(fPortfolio)
library(purrr)
returns = data.frame(returns)

colnames(returns) <- unlist(map(colnames(returns), function(x){unlist(strsplit(x,'[.]'))[1]}))
covdata = cov(returns, use = "complete.obs")

corrdata = cor(returns, use='complete.obs')
heatmap(corrdata)
```
## 3. Portfolio Construction
```{r}

pSpec = portfolioSpec()
setTargetReturn(pSpec) <- 0.045
setSolver(pSpec) <- "solveRsocp"
print(pSpec)

```
```{r}
Constraints = c("minW=c(0,0,0,0,0,0,0,0,0)", "maxW=c(0.2,0.2,0.2,0.2,0.2,0.2,0.2,0.2,0.2)" )
efficientPortfolio(data = as.timeSeries(returns[complete.cases(returns),]), spec =  pSpec)



```
## 4. Portfolio Implementation


## 5. Portfolio Evaluation


## 6. Portfolio Revisions


